Dynamic shifts in predator diel activity due to habitat type and fear

### 2021-07-28 manuscript/manuscript.Rmd
removed naive occ from table

table1 <- records %>%
  group_by(region, vegetation_group) %>%
  mutate(sites = length(unique(station)),
         deployments = length(unique(station_year)),
         fox_count_vr = sum(fox_count),
         cat_count_vr = sum(cat_count),
         fox_present = sum(fox_pa == "present"),
         cat_present = sum(cat_pa == "present"),
         fox_naive = (fox_present / deployments),
         cat_naive = (cat_present / deployments)
         )

table1 <- table1 %>%
  select(region, vegetation_group, sites, deployments, fox_count_vr, cat_count_vr, fox_naive, cat_naive)  %>% 
  distinct() %>%
  arrange(vegetation_group, region)

@@

# make table
pander(table1, style = "simple", split.table = Inf, caption = "Summary of camera-trap deployments in unique sites within Ecological Vegetation Class groups, as well as independent counts of predator detections and naive occupancy rates, across two broad regions in south-west Victoria, Australia.", round = 2,
              col.names = c("Region", "Vegetation", "Sites", "Deployments",  "Fox counts", "Cat counts", "Fox present", "Cat present"),
)

>>>>

table1 <- records %>%
  group_by(region, vegetation_group) %>%
  mutate(sites = length(unique(station)),
         deployments = length(unique(station_year)),
         fox_count_vr = sum(fox_count),
         cat_count_vr = sum(cat_count),
         fox_present = sum(fox_pa == "present"),
         cat_present = sum(cat_pa == "present")
         )

table1 <- table1 %>%
  select(region, vegetation_group, sites, deployments, fox_count_vr, cat_count_vr)  %>% 
  distinct() %>%
  arrange(vegetation_group, region)

@@

# make table
pander(table1, style = "simple", split.table = Inf, caption = "Summary of camera-trap deployments in unique sites within Ecological Vegetation Class groups, as well as independent counts of predator detections and naive occupancy rates, across two broad regions in south-west Victoria, Australia.", round = 2,
              col.names = c("Region", "Vegetation", "Sites", "Deployments",  "Fox counts", "Cat counts"),
)

### 2021-07-28 manuscript/manuscript.tex
removed naive occ from table

\begin{longtable}[]{@{}cccccccc@{}}
\caption{Summary of camera-trap deployments in unique sites within Ecological Vegetation Class groups, as well as independent counts of predator detections and naive occupancy rates, across two broad regions in south-west Victoria, Australia.}\tabularnewline
\toprule
Region & Vegetation & Sites & Deployments & Fox counts & Cat counts & Fox present & Cat present\tabularnewline
\midrule
\endfirsthead
\toprule
Region & Vegetation & Sites & Deployments & Fox counts & Cat counts & Fox present & Cat present\tabularnewline
\midrule
\endhead
Glenelg & Dry Forest & 25 & 68 & 347 & 9 & 0.66 & 0.1\tabularnewline
Otway & Dry Forest & 111 & 310 & 341 & 158 & 0.42 & 0.28\tabularnewline
Glenelg & Heathland & 40 & 119 & 265 & 59 & 0.43 & 0.34\tabularnewline
Otway & Heathland & 3 & 9 & 8 & 6 & 0.22 & 0.44\tabularnewline
Glenelg & Heathy Woodland & 154 & 424 & 574 & 96 & 0.31 & 0.14\tabularnewline
Otway & Heathy Woodland & 82 & 256 & 160 & 66 & 0.29 & 0.14\tabularnewline
Glenelg & Herb-rich Woodland & 59 & 372 & 860 & 197 & 0.5 & 0.27\tabularnewline
Otway & Herb-rich Woodland & 2 & 6 & 3 & 2 & 0.33 & 0.17\tabularnewline
Glenelg & Lowland Forest & 383 & 1046 & 1900 & 290 & 0.46 & 0.18\tabularnewline
Otway & Lowland Forest & 52 & 162 & 190 & 35 & 0.42 & 0.14\tabularnewline
Glenelg & Swampy Scrub & 4 & 10 & 19 & 8 & 0.6 & 0.5\tabularnewline
Otway & Swampy Scrub & 36 & 97 & 64 & 88 & 0.32 & 0.33\tabularnewline
Otway & Wet Forest & 281 & 780 & 715 & 1187 & 0.31 & 0.54\tabularnewline
\bottomrule
\end{longtable}

>>>>

\begin{longtable}[]{@{}cccccc@{}}
\caption{Summary of camera-trap deployments in unique sites within Ecological Vegetation Class groups, as well as independent counts of predator detections and naive occupancy rates, across two broad regions in south-west Victoria, Australia.}\tabularnewline
\toprule
Region & Vegetation & Sites & Deployments & Fox counts & Cat counts\tabularnewline
\midrule
\endfirsthead
\toprule
Region & Vegetation & Sites & Deployments & Fox counts & Cat counts\tabularnewline
\midrule
\endhead
Glenelg & Dry Forest & 25 & 68 & 347 & 9\tabularnewline
Otway & Dry Forest & 111 & 310 & 341 & 158\tabularnewline
Glenelg & Heathland & 40 & 119 & 265 & 59\tabularnewline
Otway & Heathland & 3 & 9 & 8 & 6\tabularnewline
Glenelg & Heathy Woodland & 154 & 424 & 574 & 96\tabularnewline
Otway & Heathy Woodland & 82 & 256 & 160 & 66\tabularnewline
Glenelg & Herb-rich Woodland & 59 & 372 & 860 & 197\tabularnewline
Otway & Herb-rich Woodland & 2 & 6 & 3 & 2\tabularnewline
Glenelg & Lowland Forest & 383 & 1046 & 1900 & 290\tabularnewline
Otway & Lowland Forest & 52 & 162 & 190 & 35\tabularnewline
Glenelg & Swampy Scrub & 4 & 10 & 19 & 8\tabularnewline
Otway & Swampy Scrub & 36 & 97 & 64 & 88\tabularnewline
Otway & Wet Forest & 281 & 780 & 715 & 1187\tabularnewline
\bottomrule
\end{longtable}
